\documentclass[aspectratio=43]{beamer}
% \documentclass[aspectratio=169]{beamer}

% Title --------------------------------------------
\title[Lecture 5: Advanced topics]{\Large Advanced topics \& overview}
\author[]{Francisco Villamil}
\date[]{Research Design for Social Sciences\\MA Computational Social Science, UC3M\\Fall 2023}

\input{../beamer_preamble.tex}

\begin{document}
% ====================================================

% ----------------------------------------------------
\begin{frame}
  \titlepage
\end{frame}
% ----------------------------------------------------

% ----------------------------------------------------
\begin{frame}
\frametitle{Generalizing results}
\centering

\begin{itemize}
  \item The \BGyellow{Credibility Revolution} in social sciences
  \item What are we really learning?
  \item References:
  \begin{itemize}
    \item Egami and Hartman (2023) \href{https://doi.org/10.1017/S0003055422000880}{Elements of External Validity: Framework, Design, and Analysis}. \textit{APSR} 117(3): 1070--1088.
    \item Munger (2023) \href{https://doi.org/10.1177/20531680231187271}{Temporal validity as meta-science}. \textit{Res\&Pol} 10(3).
    \begin{itemize}
      \item See also this post: \href{https://kevinmunger.substack.com/p/generalizing-knowledge-of-twitter}{Generalizing Knowledge of Twitter to ``X''}.
    \end{itemize}
    \item Esterling, Brady, \& Schwitzgebel (2023) \href{https://osf.io/2s8w5/}{The Necessity of Construct and External Validity for Generalized Causal Claims: A Critical Review of the Literature on Quantitative Causal Inference}. Preprint.
  \end{itemize}
\end{itemize}

\end{frame}
% ----------------------------------------------------

% ----------------------------------------------------
\begin{frame}
\frametitle{Generalizing results}
\centering

\begin{itemize}
  \item \BGyellow{Construct validity}: are we really measuring what we intent to?
  \begin{itemize}
    \item is the treatment doing what we theoretically expect it to? and are we measuring the outcome correctly?
  \end{itemize}
  \item \BGyellow{External validity}: would we get the same results if we replicate this in another context?
  \begin{itemize}
    \item especially: temporal and spatial validity
  \end{itemize}
\end{itemize}

\end{frame}
% ----------------------------------------------------

% ====================================================
\end{document}
